\chapter{Overall Description}

\section{Product perspective}
In this section we analyze a list of real 
scenariosand diagrams illustrating further details about shared phenomenas.\\

\subsection{Scenarios}
\begin{enumerate}
    \item \textbf{Registration} \\
    Prof. White reads about CodeKataBattle in a online spot and decides to use the platform to 
    challenge his students. So, he creates an account using his email address and personal information
     and convinces his colleagues to join the platform.\\
     Alice and her classmates, after prof. White's lesson, are interested in improving their coding 
     skills and sign up to CKB. Alice provides her email address and personal information; after the email 
     confimation goes well, 
     she can complete the registration process by linking her CKB account to her GitHub account. Her nickname
      on the platform will be her GitHub one.\\
      After the registration, both Prof. White and Alice can visualize the profile of all the other
      students and the information about the ongoing tournaments.
    \item \textbf{Creation of tournaments} \\
    Prof. Brown and prof. Smith want to decide whose class is better at programming. So Prof.Brown
    create a tournament on CKB and invite his colleague to create battles within the tournament. Prof. Brown
    sets a deadline by which their students can subscribe. A notification is sent to all CKB students. \\
    
    \item \textbf{Creation of battles} \\
    Prof. Bloom has been granted the permission to create battles in a tournament, so he uploads a 
    code kata battle. First he writes a brief textual description of the exercise, then he includes 
    the software project with build automation scripts and test cases. He also sets some rules:
    minimum and maximum number of students per group, registration deadline, final submission deadline, 
    automated evaluation parameters.\\
    Finally, he chooses to include some optional manual evaluation of his students' work.\\
    \item \textbf{Students join a battle} \\
    Bob registered to the CKB platform and received a notification about an interesting tournament 
    and he subscribed to it. 
    \\He is notified about a new interesting battle in that tournament is upcoming. Before the registration 
    deadline expires, Bob can form a group, so invites his girlfriend Eva to join him. After the registration
     deadline ends, they are sent the link of the GitHub repository of the code kata. To be able to start 
     working on the project, Bob and Eva must fork the repository and set up an automated workflow through
     GitHub Actions to inform the CKB platform about their commits.\\

    \item \textbf{Upload of a solution} \\
    Charlie has joined a battle with his friends and thinks that they have found a good solution to 
    the assigned problem. So he push his code before the final deadline to the main branch of their
    repository. \\This battle doesn't expect any manual evaluation by the educator, so as soon as 
    push the solution, the platform evaluates it and they can visualize their updated battle score.
    After the final deadline has expired, Charlie can also see the current tournament ranking. \\

    \item \textbf{Evaluation of project}\\
    When Prof. Cooper created the battle, he decided to include manual evaluation in the battle rules:
    he wants the system to assign up to 75 points, while he will assign the remaing 25 points. 
    So, scores will always be between 0 and 100.\\
    After the final deadline, prof. Cooper can see all the groups' work and he evaluates them according
    to some personal parameters such that design quality, code cleanliness, compliance with specifications.\\

    \item \textbf{Creation of gamification badges}\\
    Prof. Moore has created a tournament and to spice things up he decides to include badges.
    These are awarded according to the rules specific by him at tournament set up time: in particular,
     he wants to reward the student with most commits and the student who have attended the most battles.\\
    The badges are assigned at the end of the tournament and the collected badges can be seen by everyone
     visiting the student's profile. \\
\end{enumerate}

\subsection{Class diagrams}

\subsection{State diagrams}

\section{Product functions}

\section{User characteristics}

\section{Assumptions, dependecies and constraints}

